\subsection{Instruction Class}
\label{sec:instruction}
The Instruction class is a generic instruction representation that contains
operands, read/write semantic information about those operands, and information
about what other registers and memory locations are affected by the operation
the instruction performs.

The purpose of an Instruction object is to join an Operation with a sequence of
Operands, and provide an interface for some common summary analyses (namely, the
read/write sets, memory access information, and control flow information).

The Operation contains knowledge about its mnemonic and sufficient semantic
details to answer the following questions:
\begin{itemize}
\item What Operands are read/written?
\item What registers are implicitly read/written?
\item What memory locations are implicitly read/written?
\item What are the possible control flow successors of this instruction?
\end{itemize}

Each Operand is an AST built from RegisterAST and Immediate leaves. For each Operand, you may determine:
\begin{itemize}
\item Registers read
\item Registers written
\item Whether memory is read or written
\item Which memory addresses are read or written, given the state of all relevant registers
\end{itemize}

Instructions should be constructed from an \code{unsigned} \code{char$\ast$}
pointing to machine language, using the InstructionDecoder class.  See
InstructionDecoder for more details. 

\begin{apient}
enum InsnCategory {
  c_CallInsn,          // procedure call (NOT system calls)
  c_ReturnInsn,        // procedure return
  c_BranchInsn,        // conditional, direct, and indirect jump/branch
  c_ConditionalInsn,   // implicitly reads condition/status flags
  c_CompareInsn,       // comparisons (includes vector comparisons)
  c_PrefetchInsn,      // cache prefetch
  c_SysEnterInsn,      // x86 sysenter
  c_SyscallInsn,       // system call
  c_InterruptInsn,     // software interrupt
  c_VectorInsn,        // operates on more than one value simultaneously
  c_GPUKernelExitInsn, // AMD GPU kernel exit
  c_TransactionalInsn, // memory transaction (fences, hardware locks, etc.)
  c_NoCategory
}
\end{apient}


\begin{apient}
Instruction (Operation::Ptr what, 
             size_t size,
             const unsigned char * raw,
             Dyninst::Architecture arch)
\end{apient}
\apidesc{ \code{what} is the opcode of the instruction, \code{size}
  contains the number of bytes occupied by the corresponding machine
  instruction, and \code{raw} contains a pointer to the buffer from which
  this \code{Instruction} object was decoded. The architecture is
  specified by \code{arch}, and may be an element from the following
  set: \code{\{Arch\_x86, Arch\_x86\_64, Arch\_ppc32, Arch\_ppc64\}}
  (as defined in \code{dyn\_regs.h}).

    Construct an Instruction from an Operation and a collection of Expressions.
    This method is not intended to be used except by the InstructionDecoder
    class, which serves as a factory class for producing Instruction objects.

    While an Instruction object may be built ``by hand'' if
    desired, using the decoding interface ensures that the operation and
    operands are a sensible combination, and that the size reported is based on
    the actual size of a legal encoding of the machine instruction represented.
}

\begin{apient}
const Operation & getOperation() const
\end{apient}
\apidesc{
    Returns the \code{Operation} used by the \code{Instruction}. See
    Section~\ref{sec:operation} for details of the \code{Operation} interface.
}

\begin{apient}
std::vector<Operand> getAllOperands() const
\end{apient}
\apidesc{
Returns the operands in the order that they were decoded.

For the instruction \code{add rax, rcx}, the operands are \code{rax},
\code{rcx}, and \code{EFLAGS}. \code{EFLAGS} is included because it
is implicitly modified to update the overflow and carry flags.   
}

\begin{apient}
std::vector<Operand> getImplicitOperands() const
\end{apient}
\apidesc{
Returns the *implicit* operands in the order that they were decoded.

For the instruction \code{add rax, rcx}, the implicit operand is
\code{EFLAGS} because it is implicitly modified to update the
overflow and carry flags.
}

\begin{apient}
std::vector<Operand> getExplicitOperands() const
\end{apient}
\apidesc{
Returns the *explicit* operands in the order that they were decoded.

For the instruction \code{add rax, rcx}, the explitic operands are \code{rax}
and \code{rcx}. \code{EFLAGS} is not included because it is *implicitly*
modified to update the overflow and carry flags.
}

\begin{apient}
void getOperands(std::vector<Operand> & operands) const
\end{apient}
\apidesc{
DEPRECATED

Use `getAllOperands()`.
}

\begin{apient}
std::vector<Operand> getDisplayOrderedOperands() const
\end{apient}
\apidesc{
  Returns a vector of non-implicit operands in printed order.
}


\begin{apient}
Operand getOperand(int index) const
\end{apient}
\apidesc{
    The \code{getOperand} method returns the operand at position \code{index},
    or an empty operand if \code{index} does not correspond to a valid operand
    in this instruction.
}

\begin{apient}
unsigned char rawByte(unsigned int index) const
\end{apient}
\apidesc{
  Returns the index$^{th}$ byte in the instruction. 
}

\begin{apient}
size_t size() const
\end{apient}
\apidesc{
Returns the size of the corresponding machine instruction, in bytes.
}

\begin{apient}
const void * ptr() const
\end{apient}
\apidesc{
Returns a pointer to the raw byte representation of the corresponding machine
instruction.
}

\begin{apient}
void getWriteSet(std::set<RegisterAST::Ptr> & regsWritten) const
\end{apient}
\apidesc{
Insert the set of registers written by the instruction into
\code{regsWritten}. The list of registers returned in
\code{regsWritten} includes registers that are explicitly written as destination
operands (like the destination of a move). It also includes registers that are
implicitly written (like the stack pointer in a push or pop instruction). It
does not include any registers used only in computing the effective address of a
write. \code{pop} \code{$\ast$eax}, for example, writes to \code{esp}, reads
\code{esp}, and reads \code{eax}, but despite the fact that \code{$\ast$eax} is
the destination operand, \code{eax} is not itself written.

For both the write set and the read set (below), it is possible to determine
whether a register is accessed implicitly or explicitly by examining the
Operands. An explicitly accessed register appears as an operand that is written
or read; also, any registers used in any address calculations are explicitly
read. Any element of the write set or read set that is not explicitly written or
read is implicitly written or read. 
}

\begin{apient}
void getReadSet(std::set<RegisterAST::Ptr> & regsRead) const
\end{apient}
\apidesc{
    Insert the set of registers read by the instruction into \code{regsRead}.

    If an operand is used to compute an effective address, the registers
    involved are read but not written, regardless of the effect on the operand.
}

\begin{apient}
bool isRead(Expression::Ptr candidate) const
\end{apient}
\apidesc{
    \code{candidate} is the subexpression to search for among the values read by
    this \code{Instruction} object.

    Returns \code{true} if \code{candidate} is read by this \code{Instruction}.
}

\begin{apient}
bool isWritten(Expression::Ptr candidate) const
\end{apient}
\apidesc{
    \code{candidate} is the subexpression to search for among the values written by
    this \code{Instruction} object.

    Returns \code{true} if \code{candidate} is written by this \code{Instruction}.
}

\begin{apient}
bool readsMemory() const
\end{apient}
\apidesc{
    Returns \code{true} if the instruction reads from at least one memory address.

    If any operand containing a \code{Dereference} object is read, the
    instruction reads the memory at that address. Also, on platforms where a
    stack pop is guaranteed to read memory, \code{readsMemory} will return
    \code{true} for a pop instruction.
}

\begin{apient}
bool writesMemory() const
\end{apient}
\apidesc{
    Returns \code{true} if the instruction writes to at least one memory address.

    If any operand containing a \code{Dereference} object is write, the
    instruction writes the memory at that address. Also, on platforms where a
    stack push is guaranteed to write memory, \code{writesMemory} will return
    \code{true} for a pop instruction.
}

\begin{apient}
void getMemoryReadOperands(std::set<Expression::Ptr> & memAccessors) const
\end{apient}
\apidesc{
    Addresses read by this instruction are inserted into \code{memAccessors}.

    The addresses read are in the form of \code{Expression}s, which may be
    evaluated once all of the registers that they use have had their values set.
    Note that this method returns ASTs representing address computations, and
    not address accesses. For instance, an instruction accessing memory through
    a register dereference would return an \code{Expression} tree containing
    just the register that determines the address being accessed, not a tree
    representing a dereference of that register. Also note that the type of this
    \code{Expression} is the type of an effective address (generally a word or
    double word), not the type of the memory being accessed. For the memory being
    accessed, use \code{getOperands} directly.
}

\begin{apient}
void getMemoryWriteOperands(std::set<Expression::Ptr> & memAccessors) const
\end{apient}
\apidesc{
    Addresses written by this instruction are inserted into \code{memAccessors}. 

    The addresses written are in the same form as those returned by
    \code{getMemoryReadOperands} above.
}

\begin{apient}
Expression::Ptr getControlFlowTarget() const
\end{apient}
\apidesc{
When called on an explicitly control-\/flow altering instruction, returns the
non-fallthrough control flow destination. When called on any other instruction,
returns \code{NULL}.

For direct absolute branch instructions, \code{getControlFlowTarget} will return
an immediate value. For direct relative branch instructions,
\code{getControlFlowTarget} will return the expression \code{PC} + offset. In
the case of indirect branches and calls, it returns a dereference of a register
(or possibly a dereference of a more complicated expression). In this case, data
flow analysis will often allow the determination of the possible targets of the
instruction. We do not do analysis beyond the single-instruction level in the
Instruction API; if other code performs this type of analysis, it may update the
information in the Dereference object using the setValue method in the
Expression interface. More details about this may be found in
Section~\ref{sec:expression} and Section~\ref{sec:dereference}.

Returns an \code{Expression} evaluating to the non-fallthrough control targets,
if any, of this instruction.
}

\begin{apient}
bool allowsFallThrough() const
\end{apient}
\apidesc{
    Returns \code{false} if control flow will unconditionally go to the result
    of \code{getControlFlowTarget} after executing this instruction.
}

\begin{apient}
std::string format(Address addr = 0)
\end{apient}
\apidesc{
    Returns the instruction as a string of assembly language. If
    \code{addr} is specified, the value of the program counter as used
    by the instruction (e.g., a branch) is set to \code{addr}. 
}

\begin{apient}
bool isValid() const
\end{apient}
\apidesc{
    Returns \code{true} if this \code{Instruction} object is valid. Invalid
    instructions indicate than an \code{InstructionDecoder} has reached the end
    of its assigned range, and that decoding should terminate.
}

\begin{apient}
bool isLegalInsn() const
\end{apient}
\apidesc{
    Returns \code{true} if this Instruction object represents a legal
    instruction, as specified by the architecture used to decode this
    instruction.
}

\begin{apient}
Architecture getArch() const
\end{apient}
\apidesc{Returns the architecture containing the instruction. As
  above, this will be an element from the set \code{\{Arch\_x86,
    Arch\_x86\_64, Arch\_ppc32, Arch\_ppc64\}}.}

\begin{apient}
InsnCategory getCategory() const
\end{apient}
\apidesc{
    Currently, the valid categories are \code{c\_CallInsn},
    \code{c\_ReturnInsn}, \code{c\_BranchInsn}, \code{c\_CompareInsn},
    \code{c\_PrefetchInsn}, \code{c\_SysEnterInsn}, \code{c\_SyscallInsn},
    \code{c\_VectorInsn}, and \code{c\_NoCategory}, as defined in
    \code{InstructionCategories.h}.
}

\begin{apient}
struct CFT {
  Expression::Ptr target;
  bool isCall;
  bool isIndirect;
  bool isConditional;
  bool isFallthrough;
}

typedef ... cftConstIter;
cftConstIter cft_begin() const;
cftConstIter cft_end() const;
\end{apient}
\apidesc{
  On certain platforms (e.g., PowerPC with conditional call/return
  instructions) the \code{getControlFlowTarget} function is
  insufficient to represent the successors of an instruction. The
  \code{cft\_begin} and \code{cft\_end} functions return iterators
  into a list of all control flow target expressions as represented by
  a list of \code{CFT} structures. In most cases,
  \code{getControlFlowTarget} suffices. 
}
