\subsection{RegisterAST Class}
\label{sec:registerAST}

A \code{RegisterAST} object represents a register contained in an operand. As a \code{RegisterAST}
is an \code{Expression}, it may contain the physical register's contents if they
are known.

\begin{apient}
  typedef dyn\_detail::boost::shared\_ptr<RegisterAST> Ptr
\end{apient}
\apidesc{ A type definition for a reference-counted pointer to a \code{RegisterAST}. }

\begin{apient}
  RegisterAST (MachRegister r)
\end{apient}
\apidesc{ Construct a register using the provided register object \code{r}. The \code{MachRegister} datatype
is Dyninst's register representation and should not be constructed manually. }

\begin{apient}
  void getChildren (vector< InstructionAST::Ptr > & children) const
\end{apient}
\apidesc{ By definition, a \code{RegisterAST} object has no children. Since a \code{RegisterAST} has no children, 
the \code{children} parameter is unchanged by this method. }

\begin{apient}
  void getUses (set< InstructionAST::Ptr > & uses)
\end{apient}
\apidesc{ By definition, the use set of a \code{RegisterAST} object is itself. This \code{RegisterAST} will be 
inserted into \code{uses}. }

\begin{apient}
  bool isUsed (InstructionAST::Ptr findMe) const
\end{apient}
\apidesc{ \code{isUsed} returns \code{true} if \code{findMe} is a \code{RegisterAST} that represents the same 
register as this \code{RegisterAST}, and \code{false} otherwise. }

\begin{apient}
  std::string format (formatStyle how = defaultStyle) const
\end{apient}
\apidesc{ The format method on a \code{RegisterAST} object returns the name associated with its ID. }

\begin{apient}
  RegisterAST makePC (Dyninst::Architecture arch) [static]
\end{apient}
\apidesc{ Utility function to get a \code{Register} object that represents the program counter. \code{makePC} 
is provided to support platform-independent control flow analysis. }

\begin{apient}
  bool operator< (const RegisterAST & rhs) const
\end{apient}
\apidesc{ We define a partial ordering on registers by their register number so that they may be placed into 
sets or other sorted containers. }

\begin{apient}
  MachRegister getID () const
\end{apient}
\apidesc{ The \code{getID} function returns underlying register represented by this AST. }

\begin{apient}
  RegisterAST::Ptr promote (const InstructionAST::Ptr reg) [static]
\end{apient}
\apidesc{ Utility function to hide aliasing complexity on platforms (IA-32) that allow addressing part 
or all of a register }


\subsection{MaskRegisterAST Class}
\label{sec:MaskRegisterAST}

Class for mask register operands. This class is the same as the RegisterAST
class except it handles the syntactial differences between register operands
and mask register operands.
