\subsection{Class Archive}\label{Archive}
This is used only on ELF platforms. This class represents an archive. This class has information of all the members in the archives.

\begin{apient}
static bool openArchive(Archive *&img, string name)
\end{apient}
\apidesc{
This factory method creates a new Archive object for an archive file on disk. This object serves as a handle to the parsed archive file. name represents the name of the archive to be parsed. The Archive object is returned in img if the parsing succeeds.
This method returns false if the given file is not an archive. The error is set
to Not\_An\_Archive. This returns true if the archive is parsed without an error. printSymtabError() should be called to get more error details.
}

\begin{apient}
static bool openArchive(Archive *&img, char *mem_image, size_t size)
\end{apient}
\apidesc{
This factory method creates a new Archive object for an archive file in memory.
This object serves as a handle to the parsed archive file. mem\_image represents the pointer to the archive to be parsed. size represents the size of the memory image. The Archive object is returned in img if the parsing succeeds.
This method returns false if the given file is not an archive. The error is set
to Not\_An\_Archive. This returns true if the archive is parsed without an error. printSymtabError() should be called to get more error details. This method is not supported currently on all ELF platforms.
}

\begin{apient}
bool getMember(Symtab *&img, string member_name)
\end{apient}
\apidesc{
This method returns the member object handle if the member exists in the archive. img corresponds to the object handle for the member.
This method returns false if the member with name member\_name does not exist else returns true.
}

\begin{apient}
bool getMemberByOffset(Symtab *&img, Offset memberOffset)
\end{apient}
\apidesc{
This method returns the member object handle if the member exists at the start offset memberOffset in the archive. img corresponds to the object handle for the member.
This method returns false if the member with name member\_name does not exist else returns true.
}

\begin{apient}
bool getAllMembers(vector <Symtab *> &members)
\end{apient}
\apidesc{
This method returns all the member object handles in the archive. Returns true on success with members containing the Symtab Objects for all the members in the archive.
}

\begin{apient}
bool isMemberInArchive(string member_name)
\end{apient}
\apidesc{
This method returns true if the member with name member\_name exists in the archive or else returns false.
}

\begin{apient}
bool findMemberWithDefinition(Symtab *&obj, string name)
\end{apient}
\apidesc{
This method retrieves the member in an archive which contains the definition to a symbol with mangled name name.
Returns true with obj containing the Symtab handle to that member or else returns false.
}

\begin{apient}
static SymtabError getLastError()
\end{apient}
\apidesc{
This method returns an error value for the previously performed operation that resulted in a failure. 
SymtabAPI sets a global error value in case of error during any operation. This call returns the last error that occurred while performing any operation.
}

\begin{apient}
static string printError(SymtabError serr)
\end{apient}
\apidesc{
This method returns a detailed description of the enum value serr in human
readable format.
}
