\subsection{Class Variable}

The Variable class represents a collection of symbols that have the same address and represent data. 

\begin{tabular}{p{1.25in}p{1.125in}p{3.125in}}
	Method name & Return type & Method description \\
	\hline
	getOffset & Offset & Offset associated with this variable. \\
	getSize & unsigned & Size of this variable in the symbol table. \\
	getAllMangledNames & vector<string> \& & Unique names of symbols pointing to this variable. \\
	getType & Type * & Type of this variable, if known. \\
	getModule & const Module * & Module that contains this variable. \\
	getRegion & Region * & Region that contains this variable. \\
\end{tabular}

\begin{apient}
bool getSymbols(vector<Symbol *> &syms) const
\end{apient}
\apidesc{
This method returns the vector of Symbols that refer to the variable.
}

\begin{apient}
bool setModule (Module *module)
\end{apient}
\apidesc{
This method changes the module to which the variable belongs. Returns true if it succeeds.
}

\begin{apient}
bool setSize (unsigned size)
\end{apient}
\apidesc{
This method changes the size of the variable to size. Returns true if it succeeds.
}

\begin{apient}
bool setOffset (Offset offset)
\end{apient}
\apidesc{
The method changes the offset of the variable. Returns true if it succeeds.
}

\begin{apient}
bool addMangledName(string name, bool isPrimary)
\end{apient}
\apidesc{
This method adds a mangled name name to the variable. If isPrimary is true then it becomes the default name for the variable.
This method returns true on success and false on failure.
}

\begin{apient}
bool addPrettyName(string name, bool isPrimary)
\end{apient}
\apidesc{
This method adds a pretty name name to the variable. If isPrimary is true then it becomes the default name for the variable. 
This method returns true on success and false on failure.
}

\begin{apient}
bool addTypedName(string name, bool isPrimary)
\end{apient}
\apidesc{
This method adds a typed name name to the variable. If isPrimary is true then it becomes the default name for the variable. 
This method returns true on success and false on failure.
}


\begin{apient}
bool setType(Type *type)
\end{apient}
\apidesc{
Sets the type of the variable to type.
}
