\code{BPatch\_sourceObj} is the base class for
\code{BPatch\_function}, \code{BPatch\_module}, and \code{BPatch\_image}.
It provides a set of common methods for all three classes. In
addition, it can be used to build a "generic" source
navigator using the getObjParent and getSourceObj methods to get
parents and children of a given level (i.e. the parent
of a module is an image, and the children will be the functions).

\begin{apient}
  enum BPatchErrorLevel {
    BPatchFatal,
    BPatchSerious,
    BPatchWarning,
    BPatchInfo
  }
\end{apient}

\apidesc{
  The type of error encountered in a DyninstAPI operation.
}

\begin{apient}
  enum BPatch_sourceType {
    BPatch_sourceUnknown,
    BPatch_sourceProgram,
    BPatch_sourceModule,
    BPatch_sourceFunction,
    BPatch_sourceOuterLoop,
    BPatch_sourceLoop,
    BPatch_sourceStatement
  }
\end{apient}

\apidesc{
  The type of source statement.
}

\begin{apient}
  BPatch_sourceType getSrcType()
\end{apient}

\apidesc{
  Returns the type of the current source object.
}

\begin{apient}
  void getSourceObj(std::vector<BPatch_sourceObj *> &objs)
\end{apient}

\apidesc{
  Returns the child source objects of the current source object. For
  example, when called on a \code{BPatch\_sourceProgram}
  object this will return objects of type \code{BPatch\_sourceFunction}. When
  called on a \code{BPatch\_sourceFunction} object it may
  return \code{BPatch\_sourceOuterLoop} and \code{BPatch\_sourceStatement} objects.
}

\begin{apient}
  BPatch_sourceObj *getObjParent()
\end{apient}

\apidesc{
  Return the parent source object of the current source object. The
  parent of a \code{BPatch\_­image} is NULL.
}

\begin{apient}
  enum BPatch_language {
    BPatch_c,
    BPatch_cPlusPlus,
    BPatch_fortran,
    BPatch_fortran77,
    BPatch_fortran90,
    BPatch_f90_demangled_stabstr,
    BPatch_fortran95,
    BPatch_assembly,
    BPatch_mixed,
    BPatch_hpf,
    BPatch_java,
    BPatch_unknownLanguage
  }
\end{apient}

\apidesc{
  The programming language of the source.
}

\begin{apient}
  BPatch_language getLanguage()
\end{apient}

\apidesc{
  Return the source language of the current
  \code{BPatch\_sourceObject}. For programs that are written in more than one
  \code{BPatch\_unknownLanguage} will be returned.
}
