An object of this class represents the original executable or a library.
It serves as a container of \code{BPatch\_module} objects.

\begin{apient}
  std::string name()
  std::string pathName()
\end{apient}

\apidesc{
  Return the name of this file; either just the file name or the
  fully path-qualified name.
}

\begin{apient}
  Dyninst::Address fileOffsetToAddr(Dyninst::Offset offset)
\end{apient}

\apidesc{
  Convert the provided offset into the file into a full address in memory.
}

\begin{apient}
  struct Region {
    typedef enum {
      UNKNOWN,
      CODE,
      DATA
    } type_t;
    Dyninst::Address base;
    unsigned long size;
    type_t type;
  }
\end{apient}

\apidesc{
  A contiguous sequence of addresses that represents either code or data.
}

\begin{apient}
  void regions(std::vector<Region> &regions)
\end{apient}

\apidesc{
  Returns information about the address ranges occupied by this
  object in memory.
}

\begin{apient}
  void modules(std::vector<BPatch_module *> &modules)
\end{apient}

\apidesc{
  Returns the modules contained in this object.
}

\begin{apient}
  bool findPoints(Dyninst::Address addr, std::vector<BPatch_point *> &points)
\end{apient}

\apidesc{
  Return a vector of \code{BPatch\_points} that correspond with the
  provided address, one per function that includes an
  instruction at that address. There will be one element if there is
  not overlapping code.
}

\begin{apient}
  std::vector<BPatch_function*> *
  findFunction(const char *name, std::vector<BPatch_function*> &funcs,
               bool notify_on_failure = true, bool regex_case_sensitive = true,
               bool incUninstrumentable = false)
\end{apient}

\apidesc{
  Return a vector of \code{BPatch\_function}s matching name, or NULL
  if the function does not exist. If name contains a
  POSIX-extended regular expression, a regex search will be performed
  on function names, and matching \code{BPatch\_function}s
  returned.
  If the incUninstrumentable flag is set, the returned table of
  procedures will include uninstrumentable functions. The
  default behavior is to omit these functions.

  [NOTE: If name is not found to match any demangled function names
    in the \code{BPatch\_object}, the search is repeated as if
    name is a mangled function name. If this second search succeeds,
    functions with mangled names matching name are
  returned instead.]
}
