The Dyninst type system is based on the notion of structural equivalence. Structural
equivalence was selected to allow the system the greatest flexibility in allowing
users to write mutators that work with applications compiled both with and without
debugging symbols enabled. Using the \code{create*} methods of the \code{BPatch\ class}, a
mutator can construct type definitions for existing mutatee structures. This information
allows a mutator to read and write complex types even if the application program
has been compiled without debugging information. However, if the application has
been compiled with debugging information, Dyninst will verify the type
compatibility of the operations performed by the mutator.

The rules for type computability are that two types must be of the same storage
class (i.e. arrays are only compatible with other arrays) to be type compatible.
For each storage class, the following additional requirements must be met for two
types to be compatible:

\begin{apient}
Bpatch_dataScalar
\end{apient}

\apidesc{
Scalars are compatible if their names are the same (as defined by strcmp) and their
sizes are the same.
}

\begin{apient}
BPatch_dataPointer
\end{apient}

\apidesc{
Pointers are compatible if the types they point to are compatible.
}

\begin{apient}
BPatch_dataFunc
\end{apient}

\apidesc{
Functions are compatible if their return types are compatible, they have same number of
parameters, and position by position each element of the parameter list is type compatible.
}

\begin{apient}
BPatch_dataArray
\end{apient}

\apidesc{
Arrays are compatible if they have the same number of elements (regardless of their lower
and upper bounds) and the base element types are type compatible.
}

\begin{apient}
BPatch_dataEnumerated
\end{apient}

\apidesc{
Enumerated types are compatible if they have the same number of elements and the identifiers
of the elements are the same.
}

\begin{apient}
BPatch_dataStructure
BPatch_dataUnion
\end{apient}

\apidesc{
Structures and unions are compatible if they have the same number of constituent parts (fields)
and item by item each field is type compatible with the corresponds field of the other type.
}

In addition, if either of the types is the type \code{BPatch\_unknownType}, then the two types
are compatible. Variables in mutatee programs that have not been compiled with debugging symbols
(or in the symbols are in a format that the Dyninst library does not recognize) will be of type
\code{BPatch\_unknownType}.
