\subsection{EventNotify}
\index{EventNotify: : : :!}The EventNotify class is used to notify the user when
ProcControlAPI is ready to deliver a callback function. EventNotify is a
singleton class, which means only one instance of it is ever instantiated.
See Section \ref{bkm:Ref273371799}for a high level description of
notification.

EventNotify Declared In: 

PCProcess.h

EventNotify Types:

typedef void (*notify\_cb\_t\index{notify\_cb\_t, EventNotify: : : :!})()

This function signature is used for light-weight notification callback.

EventNotify Related Global Functions:

EventNotify *evNotify\index{evNotify: : : :!}()

This function returns the singleton instance of the EventNotify class.

EventNotify Member Functions:

int getFD\index{getFD, EventNotify: : : :!}()

This function returns a file descriptor. ProcControlAPI will write a byte that
will be available for reading on this file descriptor when a callback function
is ready to be invoked. Upon seeing that a byte has been written to this
file descriptor (likely via select or poll) the user should call the
Process::handleEvents\index{handleEvents, Process: : : :!} function. The user
should never actually read the byte from this file descriptor; ProcControlAPI
will handle clearing the byte after the callback function is invoked.

This function returns {}-1 on error. Upon an error a subsequent call to
getLastError returns details on the error.

void registerCB\index{registerCB, EventNotify: : : :!}(notify\_cb\_t cb)

This function registers a light-weight callback function that will be invoked
when a ProcControlAPI wishes to notify the user when a callback function is
ready to be invoked. This light-weight callback may be called by a
ProcControlAPI internal thread or from a signal handler; the user is encouraged
to keep its implementation appropriately safe for these circumstances.

void removeCB\index{removeCB, EventNotify: : : :!}(notify\_cb\_t cb)

This function removes a light-weight callback that was previously registered
with EventNotify::registerCB. ProcControlAPI will no longer invoke the cb
function after this function completes.

