\documentclass{article}
\newcommand{\ManualName}{proccontrol}

\usepackage{pgf}
\pgfrealjobname{proccontrol}

\usepackage{amssymb}

\input{../../common/doc/manual_commands.tex}

\begin{document}
\input{../../common/doc/manual_frontpage.tex}

\lstset{
  basicstyle=\ttfamily,
  keywordstyle=\ttfamily\color{purple},
  commentstyle=\ttfamily\color{lightgray},
  stringstyle=\ttfamily\color{orange},
  frame=leftline,
  % Highlight the proccontrol types like they are keywords, but in a different color
  emph={
    Process,
    Event,
    EventType
  },
  emphstyle=\color{blue}
}

\tableofcontents
\clearpage

\setcounter{secnumdepth}{5}

\section{Introduction}
  \input{Introduction}

\section{Abstractions}
  \input{Abstractions}

\section{Processes}
  ProcControlAPI offers several facilities for interacting with processes in a
  platform-independent manner.

  \subsection{Process}
    \input{API/Process}
  
    \subsubsection{Memory Permissions}
      \input{API/mem_perm}

  \subsection{ProcessSet}
    \input{API/ProcessSet}

  \subsection{AddressSet}
    \input{API/AddressSet}

\section{Threads}
  ProcControlAPI offers several facilities for interacting with threads in a
  platform-independent manner.

  \subsection{Thread}
    \input{API/Thread}

  \subsection{ThreadPool}
    \input{API/ThreadPool}

  \subsection{ThreadSet}
    \input{API/ThreadSet}

\section{Events}
  ProcControlAPI captures and delivers events from processes and threads.

  \subsection{Event}
    \input{API/Event}
  
  An \code{Event} passed to a callback function can be cast to the
  appropriate child class by inspecting the \code{EventType}.

  \subsection{EventBreakpoint}
    \input{API/EventBreakpoint}

  \subsection{EventCrash}
    \input{API/EventCrash}

  \subsection{EventExec}
    \input{API/EventExec}

  \subsection{EventExit}
    \input{API/EventExit}

  \subsection{EventForceTerminate}
    \input{API/EventForceTerminate}

  \subsection{EventFork}
    \input{API/EventFork}

  \subsection{EventLWPDestroy}
    \input{API/EventLWPDestroy}

  \subsection{EventLibrary}
    \input{API/EventLibrary}

  \subsection{EventNewLWP}
    \input{API/EventNewLWP}

  \subsection{EventNewThread}
    \input{API/EventNewThread}

  \subsection{EventNewUserThread}
    \input{API/EventNewUserThread}

  \subsection{EventPostSyscall}
    \input{API/EventPostSyscall}

  \subsection{EventPreSyscall}
    \input{API/EventPreSyscall}

  \subsection{EventRPC}
    \input{API/EventRPC}

  \subsection{EventSignal}
    \input{API/EventSignal}

  \subsection{EventSingleStep}
    \input{API/EventSingleStep}

  \subsection{EventStop}
    \input{API/EventStop}

  \subsection{EventTerminate}
    \input{API/EventTerminate}

  \subsection{EventThreadDestroy}
    \input{API/EventThreadDestroy}

  \subsection{EventUserThreadDestroy}
    \input{API/EventUserThreadDestroy}

\section{Inferior Remote Procedure Calls}

  \subsection{IRPC}
    \input {API/IRPC}

\section{Breakpoints}
  A breakpoint is a point in the code region of a target process that,
  when executed, stops the process execution and notifies ProcControlAPI.
  Upon being continued the process will resume execution at the point. A
  Breakpoint object is a handle that can represents one or more breakpoints in
  one or more processes. Upon receiving notification that a breakpoint has
  executed, ProcControlAPI will deliver a callback with an EventBreakpoint. 
  
  Some Breakpoint objects can be created as control-transfer
  breakpoints. When a process is
  continued after executing a control-transfer the process will resume at an
  alternate location, rather than at the breakpoint's
  installation point.
  
  A single Breakpoint can be inserted into multiple locations within a target
  process. This can be useful when a user has wants to perform a single action
  at multiple locations in a target process. For example, if a user wants to
  insert a breakpoint at the entry to function foo, and foo has multiple
  instantiations in a process, then a single Breakpoint can be inserted at each
  instance of foo.
  
  A single Breakpoint object can be inserted into multiple target processes at the
  same time. When a process does an operation that copies an address space,
  such as fork on UNIX, the child process will receive all Breakpoint objects
  that were installed in the parent process. 
  
  Multiple Breakpoint objects can be inserted into the same location with-in the
  same process. When this location is executed in the target process a single
  callback will be delivered, and the EventBreakpoint object will contain a
  reference to each Breakpoint inserted at the location. At most one
  control-transfer breakpoint can be inserted at any one point in a process.
  
  Due to the many-to-many nature of Breakpoints and Processes, a single
  installation of a Breakpoint can be identified by a Breakpoint, Process,
  Address triple. The functions for inserting and removing breakpoints
  (Process::addBreakpoint and Process::rmBreakpoint) need all three pieces of
  information.
  
  A Breakpoint can be a hardware breakpoint or
  a software breakpoint. A hardware
  breakpoint is typically implemented by setting special debug register in the
  process and can trigger on code execution, data reads or data write. A
  software breakpoint is typically implemented by writing a special instruction
  into a code sequence and can only be triggered by code execution. There are
  typically a limited number of hardware breakpoints available at the same time.

  \subsection{Breakpoint}
    \input{API/Breakpoint}

\section{Registers}

  \subsection{MachRegister}
    \input{API/MachRegister}

  \subsection{RegisterPool}
    \input{API/RegisterPool}

\section{System Calls}

  System calls are currently only supported on Linux.

  \subsection{MachSyscall}
    \input{API/MachSyscall}

\section{Libraries}
  ProcControlAPI offers several facilities for interacting with libraries
  both in a created address spaces as well as loading new libraries into one.

  \subsection{Library}
    \input{API/Library}  

  \subsection{LibraryPool}
    \input{API/LibraryPool}

\section{Platform-specific Features}
  The classes described in this section are all used to configure
  platform-specific features for Process objects. The three tracking classes
  (LibraryTracking, ThreadTracking, LWPTracking) all contain member functions to
  set either interrupt-driven or polling-driven handling for different events
  associated with Process objects. When interrupt-driven handling is enabled,
  the associated process may be modified to accommodate timely handling (e.g.,
  inserting breakpoints). When polling-driven handling is enabled, the
  associated process is not modified and events are handled on demand by calling
  the appropriate “refresh” member function.

  \subsection{FollowFork}
    \input{API/FollowFork}

  \subsection{LWPTracking}
    \input{API/LWPTracking}

  \subsection{LibraryTracking}
    \input{API/LibraryTracking}

  \subsection{SignalMask}
    \input{API/SignalMask}

  \subsection{ThreadTracking}
    \input{API/ThreadTracking}

\end{document}
